{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-27 paper/paper.tex
fixed introduction section title
added first paragraph of introduction

\section{Introduction to research area}
\label{sec:introduction}
\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper\cite{Barthe07} which is as follows. After the introduction the basic
terms and definitions for a multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typable in this type system is secure w.r.t the notion of
security. The proof that this holds is sketched in the following section.
In the last section the (by now) abstract framework is instantiated with a
concrete example.

>>>>

\section{Introduction to the research area}
\label{sec:introduction}
The challenge to protect the confidentiality of information processed by
a computer lead thirty years ago (c.f. \cite{Zdancewic04}) to the research
on the security information-flows, because of the shortcomings of the standard methods.
These standard methods are: Access control and encryption. Where
access control ensures that the data is only accessed by an authorized entity,
and encryption ensures that data can be securely transmitted over an insecure channel.
But all these methods cover the release of information and not the further
propagation (i.e. how the information is used after having access to it or decrypting
it). This is the place where information-flow security comes into play.

\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper\cite{Barthe07} which is as follows. After the introduction the basic
terms and definitions for a multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typable in this type system is secure w.r.t the notion of
security. The proof that this holds is sketched in the following section.
In the last section the (by now) abstract framework is instantiated with a
concrete example.
